% Chapter Template

\chapter{Introduction} % Main chapter title

\label{Chapter1}

%\lhead{Chapter 1. \emph{Introduction}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title
\lhead{\emph{Introduction}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

What am I going to do in the thesis?

\section{Background}

The background for a theory of \textit{Quantum Gravity} is set by a very famous principle, known as the \textit{Holographic Principle}. $AdS_n-CFT_{n-1}$ duality is the prime example of this principle. 

The complexity of the mathematical models that we have to deal with increases exponentially with the dimensionality of space-time. So it is fruitful to study the consequences of these principles in lower dimensions. Thus it is customary to explore the $(1+1)D$ (known as the \textit{Jachiw-Teitelboim} gravity) or $(2+1)D$ theories of gravity.  


\subsection{Holographic Principle}

The Holographic Principle is a suggests that the information content of a volume of space can be fully described by a theory defined on its boundary like a hologram encodes a three-dimensional image on a two-dimensional surface. The principle was proposed by Gerard ’t Hooft and Leonard Susskind, it emerged from studies of black hole thermodynamics and quantum gravity, challenging our intuitive understanding of space, information, and the fundamental nature of the universe. The principle implies that the degrees of freedom within a region of space are not proportional to its volume (as one might expect in a three-dimensional world) but to the area of its boundary, implying that our seemingly three-dimensional reality might be a "projection" of a lower-dimensional system. This idea has profound implications for reconciling quantum mechanics with general relativity, particularly in the context of black holes and string theory, and it underpins modern approaches to quantum gravity like the AdS/CFT correspondence.
The Holographic Principle originated from the study of black holes, specifically the paradox of information loss. In the 1970s, Stephen Hawking showed that black holes emit radiation (now called Hawking radiation) due to quantum effects near the event horizon, leading to their eventual evaporation. This process suggested that information inside the black hole might be lost, violating quantum mechanics’ principle of unitarity, which demands that information is preserved. Jacob Bekenstein’s work on black hole entropy provided a crucial clue: the entropy ( S ) of a black hole is proportional to the area ( A ) of its event horizon, not its volume. This is encapsulated in the Bekenstein-Hawking entropy formula:
$$ S = \frac{k c^3 A}{4 \hbar G}, $$
where \( k \) is Boltzmann’s constant, \( c \) is the speed of light, \( \hbar \) is the reduced Planck constant, \( G \) is the gravitational constant, and \( A = 4\pi r^2 \) for a Schwarzschild black hole with radius \( r = \frac{2GM}{c^2} \). Since entropy measures the number of microstates (or information content) of a system, this formula implies that the information inside a black hole scales with the two-dimensional area of its horizon (in Planck units, \( A/4l_p^2 \), where \( l_p = \sqrt{\frac{\hbar G}{c^3}} \) is the Planck's length), not its three-dimensional volume. This was surprising because, in most physical systems, entropy scales with volume, reflecting the number of particles or states within.
’t Hooft and Susskind generalized this observation, proposing that the information content of any region of space, not just black holes, is limited by the area of its boundary. Specifically, the maximum entropy in a region enclosed by a surface of area ( A ) is given by the Bekenstein bound:
$$ S \leq \frac{k c^3 A}{4 \hbar G}. $$
This bound suggests that the number of quantum states (or bits of information) needed to describe everything inside a volume is encoded on its boundary, with roughly one bit per Planck area (\( l_p^2 \)). For example, a spherical region of radius \( r \) has a boundary area \( A = 4\pi r^2 \), so its maximum entropy is proportional to \( r^2 \), not \( r^3 \). This is the essence of the Holographic Principle: the physics of a \( d \)-dimensional volume can be described by a theory in \( d-1 \) dimensions on its boundary, much like a hologram projects a 3D image from a 2D film.
The principle gained traction with the development of the AdS/CFT correspondence, proposed by Juan Maldacena in 1997, which provides a concrete realization of holography. AdS/CFT conjectures a duality between a gravitational theory in ( d )-dimensional Anti-de Sitter (AdS) space (a universe with a negative cosmological constant) and a conformal field theory (CFT) on its ( (d-1) )-dimensional boundary. For instance, in the most studied case, type IIB string theory in \( AdS_5 \times S^5 \) (a five-dimensional AdS space times a five-dimensional sphere) is dual to a four-dimensional \( \mathcal{N}=4 \) supersymmetric Yang-Mills theory on the boundary. The CFT, a quantum field theory without gravity, fully encodes the dynamics of the AdS bulk, including gravity, black holes, and quantum effects. The duality implies that bulk phenomena, like the formation of a black hole, correspond to specific states or operators in the boundary CFT. Mathematically, the partition functions of the two theories are equal:
$$ Z_{\text{AdS}} = Z_{\text{CFT}}, $$
where \( Z = \text{Tr}(e^{-\beta H}) \) is the partition function, \( H \) is the Hamiltonian, and \( \beta = 1/(k T) \). This equivalence allows physicists to study complex gravitational phenomena, like quantum gravity, using well-understood quantum field theories.
The Holographic Principle has far-reaching implications. First, it suggests that gravity, traditionally described by general relativity in the bulk, may be an emergent phenomenon arising from quantum interactions on the boundary. In AdS/CFT, the metric of the AdS space is encoded in the CFT’s correlation functions, and the radial dimension of AdS corresponds to the energy scale in the CFT via the renormalization group flow. This is often expressed through the Ryu-Takayanagi formula, which relates the entanglement entropy \( S_{\text{EE}} \) of a region in the CFT to the area of a minimal surface in the AdS bulk:
$$ S_{\text{EE}} = \frac{\text{Area of minimal surface}}{4 G \hbar}. $$
This formula generalizes the Bekenstein-Hawking entropy to arbitrary regions and highlights the deep connection between quantum entanglement and geometry.
Second, the principle challenges our understanding of spacetime. If a 3D universe can be described by a 2D boundary, the extra dimension may be an illusion, much like a hologram creates the appearance of depth. This raises questions about the fundamental nature of reality: is our universe holographic, with physical laws emerging from a lower-dimensional theory? While AdS/CFT applies to AdS spaces, efforts are underway to extend holography to flat spacetimes (like our universe) or de Sitter spaces, though these are less understood.
Third, the Holographic Principle constrains quantum gravity theories. Any consistent theory must respect the area scaling of entropy, ruling out models where information scales with volume. This has influenced string theory, loop quantum gravity, and other approaches, pushing physicists to rethink locality and causality.
Despite its elegance, the Holographic Principle faces challenges. Outside AdS/CFT, explicit holographic dualities for realistic spacetimes are lacking. The principle also raises philosophical questions: if reality is a hologram, what is the "true" dimensionality of the universe? Moreover, encoding bulk dynamics on a boundary requires non-local interactions, which are hard to reconcile with local field theories.

\subsection{AdS$_n$-CFT$_{n-1}$ Duality}

This duality is one of the most famous representation of the Holographic principle. It establishes a similarity between an $n$ dimensional AdS theory of gravity and the $n-1$ dimensional quantum theory on the surface.  

\subsubsection{AdS$_n$ spacetime}

% Writing the main content
Anti-de Sitter (AdS) spacetimes are maximally symmetric solutions to Einstein's field equations with a negative cosmological constant. These spacetimes are notably famous for the AdS/CFT correspondence and Kaluza-Klein reductions. In $D$ dimensions, AdS$_D$ has constant negative curvature and the metric is given by (in Poincaré coordinates):
\[
ds^2= e^{-2kz} \eta_{\mu\nu} dx^\mu dx^\nu + dz^2,
\] 
where $z$ is the radial coordinate, $k$ relates to the cosmological constant, and $\eta_{\mu\nu}$ is the $(D-1)$-dimensional Minkowski metric. The curvature tensors satisfy:
\[
R_{ABCD} = k^2 (\eta_{AC} \eta_{BD} - \eta_{AD} \eta_{BC}),
\]
yielding a Ricci tensor:
\[
R_{AB} = - (D-1) k^2 \eta_{AB}.
\]
The Einstein equation, with cosmological constant $\Lambda = -\frac{(D-1)(D-2)}{2} k^2$, is:
\[
R_{AB} - \frac{1}{2} R g_{AB} + \Lambda g_{AB} = 0.
\]
AdS spacetimes have a timelike conformal boundary at $z \to \infty$, which differ them from Minkowski or de Sitter spacetimes.

In gravity and Kaluza-Klein reductions, AdS spacetimes are central to brane-world scenarios, like the Randall-Sundrum model, where gravity localizes on a lower-dimensional brane within a higher-dimensional AdS bulk. A brane-world reduction from $D$-dimensional AdS gravity to $(D-1)$-dimensional gravity without a cosmological constant uses the ansatz:
\[
d\hat{s}_D^2 = e^{-2k|z|} ds_{D-1}^2 + dz^2.
\]
The $D$-dimensional Ricci tensor thus obtained is
\[
\hat{R}_{ab} = e^{2k|z|} R_{ab} - (D-1) k^2 \eta_{ab} + 2k \delta(z) \eta_{ab},
\]
\[
\hat{R}_{zz} = - (D-1) k^2 + 2k (D-1) \delta(z).
\]
If the bulk satisfies $\hat{R}_{AB} = - (D-1) k^2 \eta_{AB}$, the $(D-1)$-dimensional metric satisfies $R_{ab} = 0$, indicating pure Einstein gravity. Delta-function terms are attributed to brane sources, ensuring consistency.

AdS spacetimes also appear in sphere reductions, such as $D=11$ supergravity on $S^4$, yielding $SO(5)$-gauged supergravity in $D=7$. The AdS$_7 \times S^4$ background arises from the negative cosmological constant induced by the 4-form field strength. 

%The bosonic Lagrangian includes:
%\[
%\mathcal{L}_7 = \hat{R} * 1 - \frac{1}{4} T_{ij}^{-1} * D T_{jk} \wedge T_{k\ell}^{-1} D T_{\ell i} - V * 1,
%\]
%with potential:
%\[
%V = \frac{1}{2} g^2 \left(2 T_{ij} T_{ij} - (T_{ii})^2\right).
%\]
%This AdS geometry facilitates consistent truncation to massless modes, vital for holography and unified theories.

\subsubsection{CFT$_{n-1}$}

% Introducing Conformal Field Theory
Conformal Field Theory (CFT) refers to the field theories which are invariant under conformal transformations. A conformal transformation is a coordinate transformation that preserve angles but rescale the metric by a factor $\Omega^2(\sigma)$. Thus for a metric $g_{\alpha\beta}$, a conformal transformation satisfies:
\begin{equation}
g_{\alpha\beta}(\sigma) \to \Omega^2(\sigma) g_{\alpha\beta}(\sigma).
\end{equation}
This scale invariance ensures that the physics is same across all length scales, making CFTs essential for modeling critical phenomena in statistical mechanics and worldsheet dynamics in string theory. A conformal group is the group of all the conformal transformations (translations, dilatations and rotation). In 2D, the conformal group is infinite-dimensional, comprising holomorphic transformations $z \to f(z)$. This leads to the Virasoro algebra, with generators $L_n$ containing symmetries such as translations ($z \to z + a$) and dilatations ($z \to \zeta z$).

% Key Features
A key feature of CFTs is the absence of massive excitations, because a mass term would violate scale invariance. Instead, the focus is on correlation functions and operator transformations. The stress-energy tensor $T_{\alpha\beta}$, is traceless in conformal theories:
\begin{equation}
T^\alpha_\alpha = 0.
\end{equation}
In complex coordinates $z = \sigma^1 + i\sigma^2$, the tensor splits into holomorphic $T_{zz}(z) = T(z)$ and antiholomorphic $T_{\bar{z}\bar{z}}(\bar{z}) = \bar{T}(\bar{z})$ components, which satisfy the conservation laws $\bar{\partial} T(z) = 0$ and $\partial \bar{T}(\bar{z}) = 0$. The operator product expansion (OPE) is a key tool, expressing the product of operators at nearby points:
\begin{equation}
\mathcal{O}_i(z, \bar{z}) \mathcal{O}_j(w, \bar{w}) = \sum_k C_{ij}^k(z-w, \bar{z}-\bar{w}) \mathcal{O}_k(w, \bar{w}).
\end{equation}
Primary operators with weights $(h, \bar{h})$ have transformation form as given below (under conformal symmetries):
\begin{equation}
\mathcal{O}(z, \bar{z}) \to \left(\frac{\partial \bar{z}}{\partial z}\right)^{-h} \left(\frac{\partial \bar{\bar{z}}}{\partial \bar{z}}\right)^{-\bar{h}} \mathcal{O}(\bar{z}, \bar{\bar{z}}).
\end{equation}
These weights define the scaling dimension $\Delta = h + \bar{h}$ and spin $s = h - \bar{h}$.

% Quantum Aspects
In the quantum regime, two-dimensional CFTs are exactly solvable. The central charge $c$ in the Virasoro algebra:
\begin{equation}
[L_m, L_n] = (m-n)L_{m+n} + \frac{c}{12}m(m^2-1)\delta_{m+n,0},
\end{equation}
quantifies degrees of freedom, where the trace of the stress-energy tensor in curved space is given by:
\begin{equation}
\langle T^\alpha_\alpha \rangle = -\frac{c}{12} R.
\end{equation}

% Applications
In string theory, CFTs describe the worldsheet, ensuring gauge invariance in the Polyakov formalism. Boundary CFTs, relevant for open strings, impose conditions like $T_{zz} = T_{\bar{z}\bar{z}}$ at the boundary, reducing the number of states. The free scalar field, with action:
\begin{equation}
S = \frac{1}{4\pi\alpha'} \int d^2\sigma \partial_\alpha X \partial^\alpha X,
\end{equation}
illustrates these concepts, its propagator revealing conformal properties via the OPE. CFTs thus bridge symmetry principles with physical predictions, offering profound insights into quantum field theory and string theory.


\subsubsection{AdS/CFT correspondence}

AdS/CFT Duality Explanation
The AdS/CFT correspondence, a cornerstone of modern theoretical physics, posits a duality between a conformal field theory (CFT) in ( d )-dimensional Minkowski space and a gravitational theory in ( (d+1) )-dimensional Anti-de Sitter (AdS) space. Introduced by Maldacena, this holographic principle suggests that a strongly coupled CFT, such as \( \mathcal{N}=4 \) super Yang-Mills (SYM) in four dimensions, is equivalent to a weakly coupled supergravity theory in \( AdS_5 \times S^5 \). The correspondence leverages the isometry group \( SO(2,4) \) of \( AdS_5 \), which matches the conformal group of the CFT, enabling a dictionary between CFT operators and AdS fields. For instance, a CFT operator \( O(x) \) with conformal dimension \( \Delta \) couples to a bulk field \( \phi(x, u) \) via boundary interactions, described by the action term \( \int d^4 x , \phi_0(x) O(x) \), where \( \phi_0(x) \) is the boundary value of \( \phi \). Correlation functions in the CFT are computed using the bulk partition function, approximated classically as \[Z_{\text{AdS}}[\phi_0] = e^{-S_{\text{AdS}}[\phi]} \approx \langle e^{\int \phi_0 O} \rangle_{\text{CFT}}\] The large ( N ) limit of the gauge theory, with ’t Hooft coupling \( \lambda = g_{\text{YM}}^2 N \), corresponds to the classical supergravity limit when \( \lambda \gg 1 \), while the string coupling \( g_s \sim 1/N \). This duality allows quantum effects in the CFT, like correlation functions \[\langle O(x_1) \cdots O(x_n) \rangle\] to be computed via classical gravitational dynamics, providing insights into strongly coupled systems, confinement, and even condensed matter physics, by mapping complex quantum phenomena to tractable geometric problems in AdS space.

\subsection{$AdS_2$-CFT$_1$ correspondence}

\subsubsection{2D gravity models - JT gravity}
Jackiw-Teitelboim (JT) gravity is a model of two-dimensional (2D) gravity that provides a valuable framework for understanding quantum gravity and black hole thermodynamics in a simplified setting. Unlike in four dimensions where Einstein's equations produce dynamic degrees of freedom for the metric, in 2D spacetime the Einstein tensor vanishes identically due to topological constraints. Specifically, for any 2D metric $g_{\mu\nu}$, the Einstein tensor $G_{\mu\nu} = R_{\mu\nu} - \frac{1}{2}g_{\mu\nu}R$ is identically zero because the Ricci tensor $R_{\mu\nu}$ is completely determined by the scalar curvature $R$, and the variation of the Einstein-Hilbert action yields no dynamics. Therefore, to have a nontrivial theory of gravity in 2D, auxiliary fields such as the *dilaton* $\phi$ are introduced.

In JT gravity, the action is constructed as

$$
S_{\text{JT}} = \int d^2x \sqrt{-g} \, \phi (R + 2\Lambda),
$$

where $\phi$ is the dilaton field, $R$ is the Ricci scalar of the 2D spacetime metric $g_{\mu\nu}$, and $\Lambda$ is a cosmological constant (often negative, corresponding to an AdS$_2$ background). This action yields second-order field equations for the metric and first-order equations for the dilaton, making the theory solvable. Varying the action with respect to $\phi$ gives

$$
R + 2\Lambda = 0,
$$

which fixes the geometry to a constant curvature spacetime—typically anti-de Sitter (AdS$_2$) for $\Lambda < 0$. Varying the action with respect to the metric gives another equation involving derivatives of $\phi$, which governs how the dilaton profiles across the spacetime.

A key feature of JT gravity is that, despite having no propagating degrees of freedom in the metric, it supports black hole solutions, and its boundary dynamics are nontrivial. These dynamics are governed by the Schwarzian action, which appears when considering the low-energy limit of the boundary mode:

$$
S_{\text{Sch}}[f] = -C \int dt \, \{ f(t), t \},
$$

where $\{f(t), t\}$ is the Schwarzian derivative of the boundary reparametrization $f(t)$, and $C \propto \phi_r$ is related to the value of the dilaton at the boundary. This boundary action captures the low-energy dynamics of near-extremal black holes in higher-dimensional theories and connects JT gravity to the SYK model—a disordered quantum mechanical system with similar infrared behavior.

The JT model also arises from dimensional reduction of higher-dimensional gravity theories. For instance, spherically reducing four-dimensional Einstein gravity under the ansatz

$$
ds^2_{(4)} = g_{\mu\nu}(x) dx^\mu dx^\nu + \Phi^2(x) d\Omega_2^2
$$

produces an effective 2D theory for $g_{\mu\nu}$ and the scalar $\Phi$, leading to actions of the form

$$
S = \int d^2x \sqrt{-g} \left[ \Phi^2 R - \frac{1}{2} (\nabla \Phi)^2 - V(\Phi) \right],
$$

which includes the JT gravity model in specific limits where $\Phi \sim \phi$, and kinetic terms may be neglected.

The beauty of JT gravity lies in its exact solvability and the ability to study non-perturbative aspects of quantum gravity, black hole entropy, and holography in a tractable setting. The model encapsulates the essence of diffeomorphism invariance, black hole thermodynamics, and quantum effects such as Hawking radiation, despite its apparent simplicity.


\subsubsection{1D CFT model - SYK model}
The Sachdev-Ye-Kitaev (SYK) model is a quantum mechanical system of $N$ Majorana fermions $\chi_i(\tau)$ with all-to-all random $q$-body interactions, most commonly $q = 4$. Its action is given by:

$$
S = \int d\tau \left[ \frac{1}{2} \sum_{i=1}^{N} \chi_i \partial_\tau \chi_i - \frac{1}{4!} \sum_{i,j,k,l} J_{ijkl} \chi_i \chi_j \chi_k \chi_l \right],
$$

where $J_{ijkl}$ are real, antisymmetric, Gaussian-random couplings with zero mean and variance

$$
\langle J_{ijkl}^2 \rangle = \frac{3! J^2}{N^3}.
$$

At large $N$, the dominant Feynman diagrams contributing to the two-point function are “melon” diagrams, which can be resummed via a Schwinger-Dyson equation involving the full two-point function $G(\tau) = \frac{1}{N} \sum_i \langle \chi_i(\tau) \chi_i(0) \rangle$ and its self-energy $\Sigma(\tau)$:

$$
\Sigma(\tau) = J^2 G(\tau)^3, \qquad G(i\omega)^{-1} = -i\omega - \Sigma(i\omega).
$$

In the infrared (IR) limit, where $J|\tau| \gg 1$, the kinetic term $\partial_\tau$ becomes negligible and the equations become conformally invariant. The solution to the Schwinger-Dyson equations in this regime is:

$$
G(\tau) = b \frac{\text{sgn}(\tau)}{|J \tau|^{2\Delta}}, \quad \Delta = \frac{1}{4}, \quad b^4 = \frac{1}{4\pi}.
$$

This emergent conformal symmetry is spontaneously and explicitly broken, leading to the appearance of a soft mode governed by the Schwarzian action. By considering reparametrizations $\tau \to f(\tau)$, one finds that the leading IR effective action for these modes is:

$$
S_{\text{Sch}} = -\alpha_S N \int d\tau \, \text{Sch}(f(\tau), \tau), \quad \text{where} \quad \text{Sch}(f(\tau), \tau) = \frac{f'''(\tau)}{f'(\tau)} - \frac{3}{2} \left( \frac{f''(\tau)}{f'(\tau)} \right)^2.
$$

This Schwarzian action governs the breaking of reparametrization symmetry from $\text{Diff}(R)$ to $SL(2, \mathbb{R})$, and it plays a central role in the model's connection to two-dimensional dilaton gravity and holography.

The four-point function is given by a sum over ladder diagrams built from full propagators and a kernel:

$$
K(\tau_1, \tau_2; \tau_3, \tau_4) = -J^2 (q-1) G(\tau_{13}) G(\tau_{24}) G(\tau_{34})^{q-2}.
$$

This kernel acts on bilocal functions, and its eigenfunctions are the conformal partial waves $\mathcal{F}_h(\tau_i)$ of the $SL(2, \mathbb{R})$ group. The resulting four-point function in the conformal limit takes the form:

$$
\langle \chi_i(\tau_1) \chi_i(\tau_2) \chi_j(\tau_3) \chi_j(\tau_4) \rangle = G(\tau_{12})G(\tau_{34}) + \frac{1}{N} \int \frac{dh}{2\pi i} \rho(h) \mathcal{F}_h(\tau_i),
$$

with

$$
\rho(h) = \mu(h) \frac{k(h)}{1 - k(h)},
$$

where $k(h)$ are the eigenvalues of the kernel and $\mu(h)$ is a measure factor involving gamma functions. The poles of $\rho(h)$, given by $k(h) = 1$, determine the dimensions $h$ of bilinear operators exchanged in the four-point function, such as $\mathcal{O}_h = \sum_i \chi_i \partial_\tau^{2n+1} \chi_i$.

Of particular importance is the $h = 2$ mode, which corresponds to the Schwarzian sector. It leads to a divergence in the conformal four-point function and signals the need to include the full effective action, incorporating non-conformal corrections. The dominance of the $h = 2$ exchange in out-of-time-ordered correlators implies maximal quantum chaos, with a Lyapunov exponent:

$$
\lambda_L = \frac{2\pi}{\beta},
$$

which saturates the bound on chaos in quantum systems and matches the behavior of black holes in Einstein gravity. This profound connection makes the SYK model a valuable tool in exploring the AdS/CFT correspondence and quantum aspects of gravity.

\subsection{Virosoro Algebra and the Central Charge}
\label{subsection:central-charge}
The Witt algebra and the Virasoro algebra are fundamental structures in theoretical physics, particularly in conformal field theory (CFT), which describes systems with conformal symmetry, such as those in string theory or critical phenomena in statistical mechanics. The Witt algebra is an infinite-dimensional Lie algebra that captures the infinitesimal conformal transformations of the complex plane or the circle (S¹). Physically, it represents the symmetries of a system that remain invariant under angle-preserving transformations, like stretching or rotating parts of a plane while preserving its local structure. Its basis elements, labeled \(L_n\), correspond to vector fields that generate these transformations, with a Lie bracket \([L_n, L_m] = (n - m)L_{n+m}\), reflecting how these symmetries compose.

The Virasoro algebra, however, is the central player in CFT, extending the Witt algebra to account for quantum effects. In classical systems, symmetries like those in the Witt algebra are straightforward, but quantization introduces anomalies—quantum corrections that modify the symmetry algebra. The Virasoro algebra is the Witt algebra's *central extension*, meaning it adds a new element, a central charge \(Z\), to the algebra, which doesn’t transform under the symmetries but affects their composition. The modified Lie bracket becomes \([L_n, L_m] = (n - m)L_{n+m} + \delta_{n+m,0} \frac{n(n^2 - 1)}{12} Z\), where the extra term, proportional to \(Z\), appears only when \(n + m = 0\). This central charge \(Z\) is a scalar that commutes with all \(L_n\) (\([L_n, Z] = 0\)), making it “central” to the algebra.

The transition from the Witt to the Virasoro algebra is like upgrading a classical machine to a quantum one: the Witt algebra handles the smooth, classical symmetries, but the Virasoro algebra, with its central charge, captures the richer, quantum-deformed structure. This extension is unique (up to equivalence), making the Virasoro algebra the universal framework for describing conformal symmetries in quantum physics, with the central charge acting as a fingerprint of the system’s quantum nature.

We have adopted the following approach to compute the central-charge. From the twisted stress-energy tensor, we can compute the central charge using the following formula:

\begin{equation}
    \label{eqn:central-charge-transformation-eqn}
    \delta_{\epsilon}T_{zz}(z) = \frac{c}{12}\partial^3_z\eta(z) + 2\partial_z\eta(z)T_{zz}(z) + \eta(z)\partial_zT_{zz}(z)
\end{equation}



%\section{Organization of the Thesis}
%
%This is how acronym is added \ac{EBSD}. The present dissertation is divided into eight chapters, each of which is further divided into well-structured sections and subsections. \autoref{Chapter1} explains the rationale behind the dissertation and its objectives. \autoref{Chapter2} says something more. 
%
