% Chapter Template

\chapter{ModMax lagrangian and comparision between central charge in 2D and 3D} % Main chapter title

\label{Chapter3} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Chapter 3. \emph{ModMax Central charge}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title


\section{4D to 3D reduction and central charge}
We start with the 4D action for $EH$ gravity coupled to \textit{ModMax} electrodynamics \cite{rathi2023ads2} given by \ref{eqn:modmax-lagrangian}. We then perform suitable dimensional reduction to obtain the action in 3D and solve for the system thereafter. 


\subsection{Reduction of the ModMax Lagrangian and bulk action}
\label{subsec:modmax-4d-to-3d}
The ansatz for the metric is taken to be 
\begin{equation}
    \label{eqn:4d-3d-metric-ansatz}
    ds_{(4)}^2 = e^{2\alpha\phi}ds_{(3)}^2+e^{2\beta\phi}(dx^3)^2
\end{equation}
\begin{equation}
    dx_{(3)}^2 = g_{\mu\nu}(x^\rho)dx^\mu dx^\nu
\end{equation}
\begin{equation}
    R_{(4)} = e^{-2\alpha\phi} \left ( R_{(3)} - \frac{1}{2} (\partial\phi)^2 - d\alpha \Box\phi \right )
\end{equation}
$\mu, \nu$ are indices representing reduced dimensions and $x^3$ is the compact dimension. Note that we can drop the dalembertian term in the Ricci scalar as it is a total derivative. 

Further for this form of choice for dissection of the metric to one lower dimension (from $d+1$ to $d$), we observe that $\mathcal{L}$ becomes $e^{(\beta+(d-2)\alpha)\phi}\sqrt{-g}\mathcal{R}+\hdots \text{ where } \mathcal{R}$ is the Ricci scalar in $d$ dimensions. So it is required to set $\beta+(d-2)\alpha=0$, which gives us $\beta=-\alpha$ in $4D$ to $3D$ reduction. Further to ensure that we obtain a term of the form $\frac{1}{2}\sqrt{-g}\left(\partial\phi\right)^2 $  in the action we require $\alpha^2 = \displaystyle\frac{1}{2(d-1)(d-2)}$ which gives $\alpha = \frac{1}{2}$ for our case. The reduced metric determinant can be determined using 
\begin{equation*}
    \sqrt{-g_{(4)}} = \sqrt{-g_{(3)}}e^{(\beta+d\alpha)\phi} = e^{2\alpha\phi}\sqrt{-g_{(3)}}
\end{equation*}
The 3D projected \textit{ModMax} lagrangian can now be calculated as
\begin{align*}
    s&=\frac{1}{2}F_{AB}F^{AB} = \frac{1}{2}F_{AB}F_{CD}g^{AC}g^{BD}\\ 
     &= \frac{1}{2}F_{\mu\nu}F^{\alpha\beta}g^{\mu\alpha}g^{\nu\beta} + e^{-2\beta\phi}\left(F_{M3}F_{P3}g^{PM}\right) \\ 
    &=\frac{1}{2}F_{\mu\nu}F^{\mu\nu} + e^{-2\beta\phi}(\partial_{\mu}\chi)^2
\end{align*}
\begin{align*}
    p&=\frac{1}{2}F_{AB}\tilde{F}^{AB} = \frac{1}{2}F_{AB}F_{CD}\epsilon^{ABCD} \\ 
    &= 2e^{-2\beta\phi}\sqrt{-g_{(3)}} \left ( F_{01}F_{23} + F_{02}F_{31} + F_{21}F_{03} \right ) \\ 
    &= e^{-2\beta\phi}\epsilon^{abc}F_{ab}F_{c3} \\ 
    &= 2e^{-2\beta\phi}\epsilon^{abc}F_{ab}\partial_{c}\chi
\end{align*}
\begin{equation}
    \mathcal{L}_{\text{MM}}^{(3)} = \frac{1}{2}\left(s\cosh\zeta - \sqrt{s^2 + p^2}\sinh\zeta\right)
\end{equation}
here $\zeta$ is the \textit{ModMax} parameter.

\subsection{Equations of motion}
The 4D lagrangian is integrated along the compact dimension and we get the 3D reduced action as  
\begin{equation}
    I = \frac{1}{16\pi G_3}\int d^3x\sqrt{-g_{(3)}} \left(R - 2\Lambda - 4\kappa\mathcal{L}_{\text{MM}}^{(3)}\right)
\end{equation}
The variation of the action yields (and setting them all to zero to find the stationary action) 
\begin{equation}
    \delta I = \frac{1}{16\pi G_3}\int d^3x \sqrt{-g} \left ( \Psi_{\mu\nu}\delta g^{\mu\nu} + \Psi_\mu \delta A^\mu + \Psi_\phi \delta \phi + \Psi_\chi \delta \chi \right) 
\end{equation}
where 
\begin{align}
    \Psi_\phi &= -2\kappa \left [ -2\beta e^{-2\beta\phi} (\partial \chi)^2\cosh\zeta + \frac{\sinh\zeta}{\sqrt{s^2+p^2} } \left ( s e^{-2\beta\phi} (\partial \chi)^2 + p^2\right) \right ] = 0\\ 
    \Psi_\chi &= -4\kappa \nabla_\mu \left [-e^{-2\beta\phi} \partial^\mu \chi \cosh\zeta + e^{-2\beta\phi}\frac{\sinh\zeta}{\sqrt{s^2+p^2} } \left ( s (\partial \chi)^2 + \frac{p}{2}\epsilon^{ab\mu}F_{ab}\right)  \right ] = 0 \\ 
    \Psi_\nu &= 4\kappa \nabla_\mu \left [ F^\mu_\nu\cosh\zeta -  \frac{\sinh\zeta}{\sqrt{s^2+p^2} } \left ( s F^\mu_\nu + p e^{-2\beta\phi}\epsilon^{\mu bc}g_{b\nu}\partial_c\chi\right) \right ] = 0 \\ 
    \label{eqn:metric-variation}
    \Psi_{\mu\nu} &= \left ( R_{\mu\nu} - \frac{1}{2}g_{\mu\nu}R \right ) + \Lambda g_{\mu\nu} + 2\kappa \mathcal{L}_{MM}g_{\mu\nu} - \\ & \kappa \left [ 2 \left ( \cosh \zeta - \frac{s \sinh \zeta}{\sqrt{s^2+p^2} } \right ) \left ( F^\beta_\mu F_{\nu\beta} + e^{-2\beta\phi}\partial_\mu\chi\partial_\nu\chi \right ) - \frac{p^2\sinh\zeta}{\sqrt{p^2+s^2} }g_{\mu\nu}\right ] = 0
\end{align}
We can extract some information from the Eq~\ref{eqn:metric-variation} upon contracting it with the contravariant metric tensor. We thus obtain 
\begin{equation}
    -\frac{R}{2} + 3\Lambda -2\kappa \left [-3\mathcal{L}_{MM} + 2 \left ( \cosh \zeta - \frac{s \sinh \zeta}{\sqrt{s^2+p^2} } \right ) \left ( F^2 + e^{-2\beta\phi} (\partial \chi)^2\right ) - \frac{3p^2}{\sqrt{p^2+s^2} }\sinh\zeta \right ] = 0
\end{equation}


\subsection{Perturbative solutions in FG gauge}
In the FG gauge, upon expanding the fields 
\begin{equation}
    \Xi = \Xi^{(0)} + \kappa \Xi^{(1)} + \gamma \kappa \Xi^{(2)} + \kappa^2 \Xi^{(3)} + ...
\end{equation}
\begin{equation}
    \Sigma = \Sigma^{(1)} + \gamma \Sigma^{(2)} + \kappa \Sigma^{(3)} + ...
\end{equation}
here $\Xi$ represents the metric field and the dilaton field whereas $\Sigma$ denotes the reduced gauge field and the auxiliary scalar field coming from the $A_\mu$ term. 

Now if we expand the fields according to the above expansion and collect like order terms then we obtain the following equations 
\subsubsection{Zero order}
\begin{align}
    R^{(0)} = 6\Lambda \\ 
    G_{\mu\nu}^{(0)} + \Lambda g_{\mu\nu}^{(0)} = 0
\end{align}
All the dynamical variables are from the reduced 3D space. We note that the zeroth order equations are in agreement with the equations we obtain from the EH action for 3D AdS space. 


\subsubsection{First order}
\begin{align}
    \nabla_{\mu}& \Biggl ( -e^{-2\beta\phi^{(0)}} \partial^\mu\chi^{(1)}\cosh\zeta + \frac{e^{-2\beta\phi^{(0)}}\sinh\zeta}{\sqrt{(s^{(1)})^2 + (p^{(1)})^2} } \times \nonumber \\ & \left ( s^{(0)}\partial^\mu\chi^{(1)} + p^{(0)}/2 \epsilon^{ab\mu}{F^{(1)}}_{ab}\right ) \Biggl ) = 0 \\
    \nabla_{\mu}& \Biggl ( {F^{(1)}}^\mu_\nu\cosh\zeta - \frac{\sinh\zeta}{\sqrt{(s^{(1)})^2 + (p^{(1)})^2} } \times \nonumber \\ & \left ( s^{(0)}(F^{(1)})^\mu_\nu + p^{(1)}e^{-2\beta\phi}\epsilon^{\mu bc}(g^{(0)})_{b\nu} \partial_c \chi^{(1)}\right ) \Biggl ) = 0 \\ 
2\mathcal{L}^{(1)}_{MM} - &2 \left ( \cosh \zeta - \frac{s^{(1)}\sinh\zeta}{\sqrt{s^2+p^2} } \right ) \left ( {F^{(1)}}^\beta_\mu {F^{(1)}_{\nu\beta}} + e^{-2\beta\phi^{(0)}}\partial_\mu\chi^{(1)}\partial_\nu\chi^{(1)} \right ) - \nonumber \\ & \frac{(p^{(1)})^2}{\sqrt{(s^{(1)})^2+(p^{(1)})^2}\sinh\zeta {g^{(0)}_{\mu\nu}} } = 0
\end{align}

Contracting the last of the above equations by $g^{\mu\nu}$ gives 
\begin{equation}
    2\mathcal{L}^{(1)}_{MM} - \left ( \cosh \zeta - \frac{s^{(1)}\sinh\zeta}{\sqrt{s^2+p^2} } \right ) \left ( {F^{(1)}}^2 + e^{-2\beta\phi^{(0)}}(\partial\chi)^2 \right ) - \frac{3(p^{(1)})^2}{\sqrt{(s^{(1)})^2+(p^{(1)})^2}}\sinh\zeta = 0 \nonumber
\end{equation}

These are highly coupled partial differential equations and obtaining analytical solution to them is not possible. We will have to solve them in the IR fixed point limit as done in \cite{rathi2023ads2}.

\subsection{Boundary terms and counterterms}




\section{3D to 2D reduction and central charge}
                                                    x
We further perform dimensional reduction to get the action for a 2D spacetime and compute the central charge in the 2D to be able to make a contrast with the charge obtained from the dimensional reduction of the 4D \textit{ModMax} action as mentioned in \cite{rathi2023ads2}. 

\subsection{Reduction of the ModMax Lagrangian and bulk action}
The choice of ansatz for the metric reduction as highlighted in \ref{subsec:modmax-4d-to-3d} will not word for the reduction from 3D to 2D. We thus need to choose a different form of the metric. The ansatz for the metric, in reference to \cite{Dharewa2024} and \cite{rathi2023ads2}, is taken to be 
\begin{equation}
    ds_{(3)}^2 = \mathcal{G}_{\mu\nu}dx^\mu dx^\nu + \Phi dz^2
\end{equation}
$\mu,\nu$ are the indices of the reduced spacetime and $z$ is the compact dimension with volume $L_z$. Further the ricci scalar is given by 

\begin{equation}
    R_{(3)} = \left ( R_{(2)} - \frac{1}{4}(\partial\Phi)^2 - \frac{1}{2}\Phi^{-1} \Box\Phi \right )
\end{equation}
and 
\begin{equation}
    \sqrt{-g_{(3)}} = \sqrt{-\mathcal{G}}\sqrt{ \Phi}
\end{equation}

and the action we obtain is 
\begin{equation}
    I = \frac{1}{16\pi G_2}\int d^3x\sqrt{-g_{(2)}}\sqrt{\Phi}  \left(R - 2\Lambda - 4\kappa\mathcal{L}_{\text{MM}}^{(2)}\right)
\end{equation}
where the definition of the projected \textit{ModMax} lagrangian is similar to the one written in \cite{rathi2023ads2}

%\subsection{Equations of motion}
%Varying the action we get 
%\begin{equation}
%    \delta I = \frac{1}{16\pi G_3}\int d^3x \sqrt{-g} \left ( \Psi_{\mu\nu}\delta g^{\mu\nu} + \Psi_\mu \delta A^\mu + \Psi_\phi \delta \phi + \Psi_\chi \delta \chi \right) 
%\end{equation}

%where 
%\begin{equation}
%    \Psi_
%\end{equation}
%\subsection{Perturbative solutions in FG gauge}



\section{Future work}
We were unable to solve the equations and the for the boundary terms. The 3D-2D dictionary for the \textit{ModMax} couldn't be found as well. Thus the computation of central charge could not be carried out. We could take up this task in future and try to get the relation between the charges in 2D and 3D thereby comparing the two. Further comparision with the 2D central charge calculated by \cite{rathi2023ads2} could shed some light on the dependence of dimensional reduction metric on the central charge in the lower dimension. 

